A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-11-28 paper_review/response_1.txt

RESPONSE
----------
> Done, thank you.

******************************************
Reviewer #2:

REVIEWER COMMENT
----------
Abstract
line 24: Kepl-1627Ab cannot be a "mini-Neptune" if it is same size of Neptune.
Replace with "Neptune-size" Yes, it falls within a distribution of objects in a
period-radius diagram with an average that is smaller than Neptune, but
claiming affiliation with smaller objects implies more than we know about this
planet, e.g. its mass.

RESPONSE
----------
> Point well-taken.  R_p = 3.82 +/- 0.16 R_earth, so yes, Kepler-1627 Ab is the
> same size as Neptune within 1-sigma.  All instances in the text that referred
> to Kepler-1627 Ab as a mini-Neptune have been modified to call it a
> "Neptune-sized planet" (including the manuscript's title).

@@

REVIEWER COMMENT
----------
line 25: Kepler target stars were chosen for their suitability for transiting
detection of planets in general, and for planets that are Earth-analogs in
paraticular. That involves radius, brightess. Distance and spectral types were
not direct selection criteria; this was before Gaia.

RESPONSE
----------
> Indeed.  Batalha+2010 (ApJL) discuss the selection function, which favored
> stars that were both small and bright since these stars enable the detection
> of Earth-size planets.  M dwarfs thus were generally excluded unless they
> happened to be very close.  F, G, and K stars were favored, particularly when
> they were nearby.  The sentence in L25 currently states that "The star was
> observed by the Kepler space telescope because it is nearby (d=329pc) and it
> resembles the Sun".  More directly, yes, the star was chosen because it was
> thought that it might enable the detection of small planets in the habitable
> zone.  However the underlying reason for this given how the transit S/N
> scales is that the star was relatively bright, and it also fell within a
> particular color range.  That color range (given the Batalha+2010 logg cuts)
> corresponds to Sun-like stars.  And the brightness range for Sun-like stars
> corresponds to stars within a particular distance limit.  Our claim therefore
> holds, albeit indirectly.  It also serves the more important purpose of
> informing the reader what kind of star this paper is about: a star that is at
> a distance of ~330 parsecs, and that resembles the Sun (except for its age!).

@@

REVIEWER COMMENT
----------
line 28: "main" --> "prime"

RESPONSE
----------
> Done here and throughout the manuscript, thank you.

@@

RESPONSE
----------
> FIXME FIXME TODO

REVIEWER COMMENT
----------
Section 2

Line 65: it is convention to italicize names of space missions like TESS and K2

RESPONSE
----------
> Yes, and we leave the imposition of this convention to the copy-editors at
> the journal.

@@

REVIEWER COMMENT
----------
Lines 142-144: perhaps rephrasing this would clarify that the authors did not
use Kepler-1627 as a fiducial star about which to select cluster members, and
that they restricted the analysis to one of several sub-clusters or clumps
which contained Kepler-1627.

RESPONSE
----------
> We have slightly rephrased Lines 142-144 to clarify the meaning, which is
> indeed what the reviewer has stated.

@@

REVIEWER COMMENT
----------
Figure 1: the first three panels would be more effective if they were plotted
at the same scale and with appropriately aligned axes. As such the upper right
panels are too small to be useful. Consider leaving out the Sun (which is
irrelevant) so as to have a more appropriate choice of scale to how the details
of the cluster. The purpose of the fourth panel (tangential velocities) and the
second line in the caption are unclear to me. Aren't the tangential velocities
known from Gaia proper motions and parallaxes? Why calculate them with the
assumption of common space motion? If that is done, what does it show, anyway?

RESPONSE
----------
> Thank you for these important points of feedback.
>
> The Sun has been included to clarify the direction along which parallax
> uncertainties are expected to produce erroneous clusterings (analogous to the
> "Fingers of God" effect in the extragalactic literature).  This is relevant
> because the HDBScan clustering method used by Kounkel & Covey in their 2019
> paper likely was susceptible to this systematic effect.  A sentence has been
> added to the caption of Figure 1 to clarify this point.
> 
> The {X,Y}, {Z,X}, and {Z,Y} panels are plotted at different scales in order
> to keep the aspect ratios roughly correct.  The reported KC2019 cluster
> members span {ΔX, ΔY, ΔZ} of roughly {400, 600, 200} parsecs,  which grows to
> ~{600, 600, 200} parsecs when including the Sun.  The {Z,X} and {Z,Y}
> panels should therefore roughly have aspect ratios of 1:3 in order for the
> parsec to not be stretched too much in either dimension.  The top-down {X,Y}
> view is the most informative dimension, which is why it is enlarged related
> to the edge-on views (and its 1:1 aspect ratio is set by the same
> consideration).
>
> Finally, the tangential velocities are important because they tell us whether
> the structures are kinematically coherent.  Open clusters typically have
> velocity dispersions of order ~1km/s.  Meingast et al. 2021 (A&A 645 84) for
> instance suggest tangential velocities <2 km/s (from the mean cluster
> velocity) as a plausible cutoff for selecting candidate cluster members.  One
> needs to compute these as relative tangential velocities instead of just
> looking at the proper motions because the proper motions are changed by
> line-of-sight projection effects, especially when the clusters appear
> stretched over tens of degrees on-sky.  See for instance Figure 2 of
> Meingast+2021, or Figure 14 of Bouma+2021 (AJ, 162, 197).  In our case, the
> tangential velocities indicate that the spread in Kounkel & Covey 2019's
> reported cluster members is ~10km/s, which is large enough that it does not
> make obvious kinematic sense to consider all of these stars to be part of the
> same structure.  We've added a few sentences in the manuscript to clarify
> these latter points.

@@

REVIEWER COMMENT
----------
Figure 3 bottom: Can the IC 2602 and 2391 rotation periods be added to this
plot? Lines 276-278 mention that these and cite Douglas et al. 2021 (although
the reference does not seem to be complete). Isn't it interesting that the
interlopers all fall on the Praesepe rotation sequence?

RESPONSE
----------
> Thank you for pointing out the missing link in the reference to Douglas et
> al. 2021, which should have pointed to
> https://ui.adsabs.harvard.edu/abs/2021tsc2.confE.157D/abstract, and has been
> updated in the revision.  The rotation periods from this work, which includes
> IC 2602, IC 2391, and a few other 30-50 Myr clusters, are not yet public.  
>
> The interlopers falling on the Praesepe sequence is indeed a bit odd, but
> it's really only ~3-5 stars. A much bigger set of interlopers didn't have
> detected rotation periods at all! (See final paragraph of Section 2.2.2).
> At the other reviewer's request, we've also added a sentence noting that some
> of these stars might be unresolved F+K binaries.

@@

REVIEWER COMMENT
----------
p 5 lines 258-261: rather than simply throw the TESS values out in favor of the
Kepler ones, the authors should compare them to evaluate the accuracy and
reliability of the TESS values.

RESPONSE
----------
> Thank you for this point -- please see kepler_vs_tess_prot.png in the
> attached, which shows the 28 referenced stars that overlap.  5 of the 28
> stars have Kepler rotation periods above 10 days, of which none were
> correctly recovered by TESS (3 are chosen at the half-period harmonic).  Of
> the 23 stars with periods below 10 days, 21 of the TESS periods agree with
> the Kepler rotation periods, and 2 are at the double-period harmonic.
>
> We've updated the text to reflect this point, which doesn't affect any of the
> conclusions given that almost all the δ Lyr cluster stars have rotation
> periods below below 10 days.

@@

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Section 4.1.3 and Figure 6

The significance of this slope is unclear and a sigma is not a good way to
evaluate it. Perform a ratio of chi-squared or F-test to evaluate it vs. a flat
line.

RESPONSE
----------
> TODO ??? WHY ISN'T SIGMA OK?  THE POINT IS THAT IT'S 2-SIGMA...

@@

REVIEWER COMMENT
----------
Lines 530-542: does option (ii) include a transit fit as well? I assume it does
but it would be good to clarify. And is option (i) the 2nd and 4th order
polynomial? Perhaps just state this?

RESPONSE
----------
> Yes, option (ii) includes the transit -- we've updated this in the text for
> clarity.
>
> Yes, option (i) is the 2nd or 4th order polynomial.  We've updated the text
> to state this more directly as well.  Thank you!

@@

REVIEWER COMMENT
----------
Line 561-562: do the authors mean "lack of statistical significance"?

RESPONSE
----------
> Yes -- we've clarified this in the text.  Thank you!

### 2021-11-28 paper/ms.tex
[WIP] reviewer #2 staging

\title{
  A 38 Million Year Old Mini-Neptune in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the main Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; their ages can be verified \replaced{through}{with} the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr \citep{meibom_kepler_2011}.
Though isochronal, gyrochronal, and lithium-based analyses suggest
that younger Kepler planets do exist
\citep{walkowicz_rotation_2013,berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia data have greatly expanded our knowledge
of cluster memberships \citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities   of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  The reported
cluster members (gray and black points) extend over a much larger
volume than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.  We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed the
selection cuts manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  \deleted{As a matter of
scope, we restricted our attention to the \nkinwithtess\ stars
discussed in Section~\ref{sec:kinematicselection} in the spatial and
kinematic proximity of Kepler\,1627.}  
Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 28 of \replaced{these }{our \nkinwithtess\ }stars; for these cases, we
simply adopted the Kepler rotation period.
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top)
and purple (bottom).  The model parameters and their uncertainties,
given in Table~\ref{tab:posterior}, are broadly consistent with a
mini-Neptune sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in
circular\footnote{ Our transit fitting yields $e<0.48$ at 2-$\sigma$;
the constraints on the eccentricity are not particularly strong.}
orbit around a G8V host star ($0.88 \pm 0.02 R_\odot$).  This best-fit
planet size is consistent with those previously reported by
\citet{morton_false_2016} and \citet{berger_2018_radii}, and
corrects for the small amount of flux dilution from Kepler\,1627B.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local polynomial baseline plus the transit, and {\it ii)} a local linear
trend.  We considered the results both for a second and fourth-order
time-dependence in the local baseline.  We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}.

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
statistical significance, this analysis should be interpreted as
suggestive at best.

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the main
Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   Could the transit
be produced by anything other than a planet orbiting this near-solar
analog?  \citet{morton_false_2016} validated the planet based on the
transit shape, arguing that the most probable false positive scenario
was that of a background eclipsing binary, which had a model-dependent
probability of $\approx$$10^{-5}$.  However, this calculation was
performed without knowledge of the low-mass stellar companion ($M_{\rm
B}\approx 0.33\,M_\odot$).  Validated planets have also previously
been refuted \citep[{\it e.g.},][]{shporer_three_2017}.  We therefore
reassessed false positive scenarios in some detail.

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019} , HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  However, smaller planets could have been
detected: the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days \citep{2021ascl.soft07027B}.  The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$ to 10$\,M_\oplus$ mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.

>>>>

\title{
  A 38 Million Year Old Neptune-Sized Planet in the Kepler Field
}

@@

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.8\,R_\oplus$ \replaced{mini-Neptune}{planet} on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show using
  Gaia kinematics, TESS stellar rotation periods, and spectroscopic
  lithium abundances that Kepler\,1627 is a member of the \clusterage\
  old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found by
  the \replaced{main}{prime} Kepler mission.  The Kepler photometry shows two
  peculiarities: the average transit profile is asymmetric, and the
  individual transit times might be correlated with the local light curve
  slope.  We discuss possible explanations for each anomaly.  More
  importantly, the $\delta$~Lyr cluster
  is one of $\sim$10$^3$ coeval groups whose properties have been clarified
  by Gaia.  Many other exoplanet hosts are candidate members
  of these clusters; their ages can be verified \replaced{through}{with} the
  trifecta of Gaia, TESS, and ground-based spectroscopy.
\end{abstract}

@@

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020,martioli_aumicbc_2021}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the \replaced{main}{prime} Kepler mission (2009--2013), only four open clusters
were known in the Kepler field,
%: NGC\,6866, NGC\,6811, NGC\,6819, and NGC\,6791,
with ages spanning 0.7\,Gyr to 9\,Gyr \citep{meibom_kepler_2011}.
Though isochronal, gyrochronal, and lithium-based analyses suggest
that younger Kepler planets do exist
\citep{walkowicz_rotation_2013,berger_identifying_2018,david_sizes_2021}, accurate and precise
age measurements typically require an ensemble of stars.  Fortunately,
recent analyses of the Gaia data have greatly expanded our knowledge
of cluster memberships \citep[{\it
e.g.},][]{CantatGaudin2018a,Zari2018,KounkelCovey2019,Meingast2021,Kerr2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

Matching our young star list against stars observed by Kepler revealed
that Kepler observed a portion of the \cn\ (Stephenson-1; Theia~73).
More specifically, a clustering analysis of the Gaia data by
\citet{KounkelCovey2019} reported that Kepler~1627 (KIC 6184894; KOI
5245) is a \cn\ member.  Given the previous statistical
validation of the close-in \replaced{mini-Neptune}{Neptune-sized
planet} Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we begin by scrutinizing the properties of the cluster
(Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr cluster is
\clusterage\ old, and in Section~\ref{sec:stars} show that \sn\ is
both a binary and also a member of the cluster.  Focusing on the
planet (Section~\ref{sec:planet}), we confirm that despite the
existence of the previously unreported M2.5V companion, hereafter
Kepler\,1627B, the planet orbits the G-dwarf primary, Kepler\,1627A.
We also analyze an asymmetry in the average transit profile, and a
possible correlation between the individual transit times and the
local light curve slope.  We conclude by discussing broader
implications for our ability to age-date a larger sample of planets
(Section~\ref{sec:conc}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities   of stars in the
    $\delta$\,Lyr cluster.} Points are reported cluster members from
    \citet{KounkelCovey2019}.  The tangential velocities relative to
    \sn\ (bottom right) are computed assuming that every star has the
    same three-dimensional spatial velocity as \sn.  Our analysis
    considers stars (black points) in the spatial and kinematic
    vicinity of Kepler\,1627 (yellow star).  The question of whether
    the other candidate cluster members (gray points) are part of the
    cluster is outside our scope.  The location of the Sun is
    ($\odot$) is shown \added{to clarify the direction along which
    parallax uncertainties are expected to produce erroneous
    clusters}.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

\citet{KounkelCovey2019} applied an unsupervised clustering algorithm
to Gaia DR2 on-sky positions, proper motions, and parallaxes for stars
within the nearest kiloparsec.  For the \cn\ (Theia 73), they reported
\noriginal\ candidate members.  We matched these stars against the
latest Gaia EDR3 observations using the \texttt{dr2\_neighbourhood}
table from the ESA archive,
taking the stars closest in proper motion and epoch-corrected angular
distance as the presumed match \citep{gaia_collaboration_2021_edr3}.
In Figure~\ref{fig:XYZvtang}, \added{we }have shown galactic positions only for
the stars with parallax signal-to-noise exceeding 20.  \added{We
calculated the tangential velocities for each of these stars relative to \sn\
($\Delta \mu^{*}$) by subtracting the observed proper motion from what the proper motion at the star's
position would be if it were co-moving with \sn. }The reported
cluster members (gray and black points) extend over a much larger
volume \added{in both physical and kinematic space }than the cluster previously identified by
\citet{stephenson_possible_1959} and later corroborated by
\citet{eggen_photometric_1968}.  While the non-uniform ``clumps'' of
stars might comprise a {\it bona fide} cluster of identically-aged
stars, they could also be heavily contaminated by field stars.
\added{One reason to suspect this is that the spread in tangential
velocities exceeds typical limits for kinematic coherence
\citep{Meingast2021}}.
We
therefore considered stars only in the immediate kinematic and spatial
vicinity of \sn\ as candidate cluster members.  We performed
\replaced{the}{this}
selection cut\deleted{s} manually, by drawing lassos with the interactive
\texttt{glue} visualization tool \citep{beaumont_2014_13866} in the
four projections shown in Figure~\ref{fig:XYZvtang}.  The overlap
between the Kepler field and the resulting candidate cluster members
is shown in Figure~\ref{fig:skychart}.  While this method will include
some field interlopers in the ``cluster star'' sample, and vice-versa,
it should suffice for our aim of verifying the existence of the
cluster in the vicinity of \sn.
%\added{The application of a more careful membership selection procedure to the $\delta$\ Lyr\ cluster (as part of a larger complex spanning Cepheus and Hercules) is a topic under current investigation by by R.~Kerr and collaborators.}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.  \deleted{As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}  \deleted{Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
\replaced{these }{our \nkinwithtess\ }stars; for these cases, we
simply adopted the Kepler rotation period.} \added{First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS (3 were near the
half-period harmonic).  We therefore adopted a general stance of
caution for TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods for the stars for which they were available.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

Figure~\ref{fig:lc} shows the resulting best-fit model in orange (top)
and purple (bottom).  The model parameters and their uncertainties,
given in Table~\ref{tab:posterior}, are broadly consistent with a
\replaced{mini-Neptune }{Neptune-}sized planet ($3.82\pm0.16\,R_\oplus$) on a close-in
circular\footnote{ Our transit fitting yields $e<0.48$ at 2-$\sigma$;
the constraints on the eccentricity are not particularly strong.}
orbit around a G8V host star ($0.88 \pm 0.02 R_\odot$).  This best-fit
planet size is consistent with those previously reported by
\citet{morton_false_2016} and \citet{berger_2018_radii}, and
corrects for the small amount of flux dilution from Kepler\,1627B.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}.

One concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
\added{lack of }statistical significance, this analysis should be interpreted as
suggestive at best.

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the
\replaced{main}{prime}
Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   Could the transit
be produced by anything other than a planet orbiting this near-solar
analog?  \citet{morton_false_2016} validated the planet based on the
transit shape, arguing that the most probable false positive scenario
was that of a background eclipsing binary, which had a model-dependent
probability of $\approx$$10^{-5}$.  However, this calculation was
performed without knowledge of the low-mass stellar companion ($M_{\rm
B}\approx 0.33\,M_\odot$).  Validated planets have also previously
been refuted \citep[{\it e.g.},][]{shporer_three_2017}.  We therefore
reassessed false positive scenarios in some detail.

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019} , HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  However, smaller planets could have been
detected: the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days \citep{2021ascl.soft07027B}.  The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$ to 10$\,M_\oplus$ mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{This of course depends on the mass of \pn; an alternative
explanation for its large size could simply be that it is more massive
than the typical Kepler mini-Neptune, or that it has an abnormally
large envelope to core mass ratio.}
